A Horrocks-type theorem for even orthogonal $K_2$

### 2020-04-09 dl-paper.tex
Minor fixes

\begin{corollary} \label{K-a-b-cor}
One has $\widetilde{K}(\alpha, \beta) = K(A[X], M[X]) \cap \widetilde{P}_{\alpha, M}(0) \cap \widetilde{P}_{\beta, M}(0)$. In particular, $\widetilde{K}(\alpha, \beta)$ and $K(\alpha, \beta)$ do not depend on the choice of the root $\delta$ in~\cref{def:Kab}.
\end{corollary}
\begin{proof} Denote $\widetilde{P}_{\alpha, M}(0) \cap \widetilde{P}_{\beta, M}(0) \cap K(A[X], M[X])$ by $K$. It is clear that $\widetilde{K}(\alpha, \beta) \subseteq K$. 
Let us prove the reverse inclusion. Let $g$ be an element of $K$.
By~\cref{K-a-b} $g$ can be presented as $g_0 \cdot x_{-\alpha}(mX) \cdot x_{-\beta}(m'X)$ for some $g_0 \in \widetilde{K}(\alpha, \beta)$ and $m, m' \in M$. From~\cref{rem:palpha} we obtain that $0 = p_\alpha(g) = m$, $0 = p_\beta(g) = m'$, therefore $g = g_0$ lies in $\widetilde{K}(\alpha, \beta)$, as required.\end{proof}

@@

We come to the central concept of this subsection.
\begin{df} Define the subgroups $P_\alpha(0)$, $P_{\alpha}(*)$ and $K(\alpha, \beta)$ of $\overline{\St}(\Phi, R, I)$ as the images of the subgroups $\widetilde{P}_{\alpha, M}(0)$, $\widetilde{P}_{\alpha, M}(*)$ and $\widetilde{K}(\alpha, \beta)$ under the natural homomorphism $j_+ \colon \St(\Phi, A[X]) \to \St(\Phi, R)$.\end{df}

>>>>

\begin{corollary} \label{K-a-b-cor}
One has $\widetilde{K}(\alpha, \beta) = K(A[X], M[X]) \cap \widetilde{P}_{\alpha, M}(0) \cap \widetilde{P}_{\beta, M}(0)$. In particular, $\widetilde{K}(\alpha, \beta)$ does not depend on the choice of the root $\delta$ in~\cref{def:Kab}.
\end{corollary}
\begin{proof} Denote $\widetilde{P}_{\alpha, M}(0) \cap \widetilde{P}_{\beta, M}(0) \cap K(A[X], M[X])$ by $K$. It is clear that $\widetilde{K}(\alpha, \beta) \subseteq K$. 
Let us prove the reverse inclusion. Let $g$ be an element of $K$.
By~\cref{K-a-b} $g$ can be presented as $g_0 \cdot x_{-\alpha}(mX) \cdot x_{-\beta}(m'X)$ for some $g_0 \in \widetilde{K}(\alpha, \beta)$ and $m, m' \in M$. From~\cref{rem:palpha} we obtain that $0 = p_\alpha(g) = m$, $0 = p_\beta(g) = m'$, therefore $g = g_0$ lies in $\widetilde{K}(\alpha, \beta)$, as required.\end{proof}

@@

\begin{df} Define the subgroups $P_\alpha(0)$, $P_{\alpha}(*)$, $K(\alpha, \beta) \leq \overline{\St}(\Phi, R, I)$ as the images of the subgroups $\widetilde{P}_{\alpha, M}(0)$, $\widetilde{P}_{\alpha, M}(*)$, $\widetilde{K}(\alpha, \beta)$ under the natural homomorphism $j_+ \colon \St(\Phi, A[X]) \to \St(\Phi, R)$.\end{df}
